---
output: 
  github_document:
    html_preview: false # https://rmarkdown.rstudio.com/github_document_format.html#HTML_Preview
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, include=FALSE,eval=TRUE}
get_theme_sha <- function(theme_dir = NULL) {
  submodule <- git2r::repository(
    path = here::here("themes", theme_dir))

  sha <- submodule |>
    git2r::repository_head() |>
    git2r::sha()
  return(sha)
}

commit_badge <- function(user = NULL, repo = NULL, sha = NULL) {
  glue::glue("[![GitHub commits since tagged version](https://img.shields.io/github/commits-since/{user}/{repo}/{sha}?style=flat&logo=github&label=Commits%20since%20last%20theme%20submodule%20pull)](https://github.com/{user}/{repo}/compare/{sha}...master)")
}
```



# [kleinbutsignificant.com](https://www.kleinbutsignificant.com)

<!-- badges: start -->
[![Netlify Status](https://api.netlify.com/api/v1/badges/7fcdb00f-8ea5-499d-a803-2a61544f74f7/deploy-status)](https://app.netlify.com/sites/kleinbutsignificant/deploys)
[![Website](https://img.shields.io/website?url=https%3A%2F%2Fwww.kleinbutsignificant.com&link=https%3A%2F%2Fwww.kleinbutsignificant.com)](https://www.kleinbutsignificant.com)
`r commit_badge(user = "adityatelange", repo = "hugo-PaperMod",
                sha = get_theme_sha(theme_dir = "PaperMod"))`

<!-- [![GitHub commits since tagged version](https://img.shields.io/github/commits-since/adityatelange/hugo-PaperMod/`r readLines(".git/modules/themes/PaperMod/refs/heads/master")`?style=flat&logo=github&label=Commits%20since%20last%20theme%20submodule%20pull)](https://github.com/adityatelange/hugo-PaperMod/compare/`r readLines(".git/modules/themes/PaperMod/refs/heads/master")`...master) -->


<!-- https://shields.io/badges/git-hub-commits-since-tagged-version -->
<!-- https://github.com/adityatelange/hugo-PaperMod/commits/master -->
<!-- https://github.com/adityatelange/hugo-PaperMod/compare/master...21ae19bc2b02089a234509bd4d4bb3a72659999a -->


![Hugo](https://img.shields.io/badge/Hugo-black.svg?style=for-the-badge&logo=Hugo)
![RStudio](https://img.shields.io/badge/RStudio-4285F4?style=for-the-badge&logo=rstudio&logoColor=white)

<!-- ![R](https://img.shields.io/badge/r-%23276DC3.svg?style=for-the-badge&logo=r&logoColor=white) -->
<!-- badges: end -->

## TODOs

- fix summary text in list cards (avoid title), instead use description field
- italics in post titles (markdown, html, or Go)
- change search logo to Mac on all platforms
- get emojis to work
- setup python environment local for blog

- start writing
  - About
- CV download
- add email contact
- add GitHub CI 
  - run `hugo -v` / `build_site` from source repo and export automatically to pages

## Hugo

- https://gohugo.io/getting-started/directory-structure/


## Python

pip install jupyter-cache
or conda-forge

## Devcontainer & GitHub Codespaces



## RStudio 

- https://github.com/rocker-org/devcontainer-features/blob/main/src/rstudio-server/install.sh
- `RSTUDIO_DATA_DIR=/usr/local/share/rocker-devcontainer-features/rstudio-server/data`

**Config:**

- /etc/rstudio/rserver.conf
- /etc/rstudio/rsession.conf
- /etc/rstudio/logging.conf
  - https://docs.posit.co/ide/server-pro/server_management/logging.html
  - -> /var/log/rstudio/rstudio-server

- https://support.posit.co/hc/en-us/articles/200552316-Configuring-the-Server

- RStudio User config: `/home/rstudio`

```
$ sudo rstudio-server verify-installation
```